### 2015-11-17 section/2_workless.tex
revise through section 3.1

\section{\Tool design}
\label{sec:design}
\Tool is composed of a series of analysis routines that
identify whether a given loop belongs to any root cause type discussed in
Section \ref{sec:study_tax}.
Its design
follows the following principles.
\begin{itemize}
\item Failure diagnosis, not bug detection. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

\item Static-dynamic hybrid analysis. As we will see, static analysis alone
will not be able to provide all the needed information. However, 
dynamic analysis alone will incur too much overhead.
Therefore, we use a hybrid approach throughout our design.

@@

Our resultless checker includes two parts. First, we use static analysis
to figure out which are the side-effect instructions in a loop and hence
decide whether a loop belongs to 0*, 0*1?, [0$|$1]*, or 1*. Second, for
0*1? and [0$|$1]* loops, we use
dynamic analysis to figure out what portion of loop iterations are
resultless at run time, which will help decide whether the loop is indeed
inefficient.

@@

Finally, since the 1* pattern contains the least amount of information
about computation \textit{inefficiency}, \Tool will not report a loop's
root-cause type as 1*, if more informative root-cause type is identified 
for this loop (e.g., cross-iteration or cross-loop redundancy).

@@

We could speed up the above counting using sampling. However, since the 
run-time overhead of the above counting is low, as shown in Section 
\ref{sec:experiment}, our current prototype of \Tool does 
not use sampling for this part of run-time analysis.

@@

\subsubsection{Limitations}
\label{sec:l_workless}
The technique designed in this section has the following limitations.
First, when callee may have side effect, we will consider it will have side effect in the caller side, 
and do not consider the real execution inside callee. This could bring false negatives, 
because we could miss resultless cases, 
where side effect instructions inside callee do not execute. 
Experiments results in Section~\ref{sec:experiment} show that this is not a big issue, 
since we do not miss any resultless bugs.

Second, our dynamic instrumentation does not consider concurrent execution of the monitored loop, 
because most of buggy loops we study only execute in one single thread. 
When the monitored loop is executed in multi-thread, like loop marked with omp pragma, we need to synchronize updates to global variables.

>>>>

\section{\Tool design}
\label{sec:design}
\Tool consists of a series of analysis that
judges whether a given loop belongs to any root cause type discussed in
Section \ref{sec:study_tax}.
Its design
follows the following principles.
\begin{itemize}
\item Failure diagnosis, not bug detection. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

\item Static-dynamic hybrid analysis. As we will see, static analysis alone
will not be able to provide all the needed information to judge whether
a loop is problematic. However, 
dynamic analysis alone will incur too much overhead.
Therefore, we use a hybrid approach throughout our design.

@@

Our resultless checker includes two parts. First, we use static analysis
to figure out which are the side-effect instructions in a loop and hence
decide whether a loop belongs to 0*, 0*1?, [0$|$1]*, or 1*. Second, to
accurately determine 0*1? and [0$|$1]* loops, we use
dynamic analysis to figure out what portion of loop iterations are
resultless at run time.
%, which will help decide whether the loop is indeed
%inefficient.

@@

Note that since the 1* pattern contains the least amount of information
about computation \textit{inefficiency}, \Tool will not report a loop's
root-cause type as 1*, if more informative root-cause type is identified 
for this loop (e.g., cross-iteration or cross-loop redundancy).

@@

\comment{
We could speed up the above counting using sampling. However, since the 
run-time overhead of the above counting is low, as shown in Section 
\ref{sec:experiment}, our current prototype of \Tool does 
not use sampling for this part of run-time analysis.
}

@@

\comment{
\subsubsection{Limitations}
\label{sec:l_workless}
When callee may have side effect, we will consider it will have side effect in the caller side, 
and do not consider the real execution inside callee. This could bring false negatives, 
because we could miss resultless cases, 
where side effect instructions inside callee do not execute. 
Experiments results in Section~\ref{sec:experiment} show that this is not a big issue, 
since we do not miss any resultless bugs.

Second, our dynamic instrumentation does not consider concurrent execution of the monitored loop, 
because most of buggy loops we study only execute in one single thread. 
When the monitored loop is executed in multi-thread, like loop marked with omp pragma, we need to synchronize updates to global variables. 
}

### 2015-11-17 section/3_redundancy.tex
revise through section 3.1

First, we identify and avoid monitoring memory reads whose return values can be 
statically proved to
not change throughout one loop instance (i.e., for cross-iteration
redundancy analysis) or multiple loop instances (i.e., for cross-loop redundancy
analysis). Since we implement \Tool at LLVM byte-code level, a major part of this
analysis is already done by LLVM, which lifts loop-invariant memory
accesses out of loops. The only extra analysis we did is to 
prune memory reads whose reading address is loop invariant, and there are no writes 
inside the loop which are possibly conducted on the same address. 
For example, the read address of \texttt{aNode.localName} and \texttt{aNode.namespaceURI}
in Figure~\ref{fig:Mozilla347306} is loop-invariant, and there are no write conducted 
on the same address. We do not need to record these two memory read. 
%It is easy to lift read from local variable outside the loop. 
%Compiler is conservative to move read, which may cause exception, outside the loop.
%I think this part of analysis is to prune memory read which is invariant, but unsafe to be moved out by compiler. 
%llvm is very conservative to move memory read from array/structure/global variable/heap variable
%outside the loop.
%what we do is if the read address is loop invariant, and there are no other write possibly 
%write to the same place, we will not record the memory read.

>>>>

First, we identify and avoid monitoring memory reads whose return values can be 
statically proved to
not change throughout one loop instance (i.e., for cross-iteration
redundancy analysis) or multiple loop instances (i.e., for cross-loop redundancy
analysis). Since we implement \Tool at LLVM byte-code level, a major part of this
analysis is already done by LLVM, which lifts loop-invariant memory
accesses out of loops. The only extra analysis we did is to 
prune memory reads whose reading address is loop invariant, and there are no writes 
inside the loop which are possibly conducted on the same address. 
For example, the read address of \texttt{aNode.localName} and \texttt{aNode.namespaceURI}
in Figure~\ref{fig:Mozilla477564} is loop-invariant, and there are no write conducted 
on the same address. We do not need to record these two memory read. 
%It is easy to lift read from local variable outside the loop. 
%Compiler is conservative to move read, which may cause exception, outside the loop.
%I think this part of analysis is to prune memory read which is invariant, but unsafe to be moved out by compiler. 
%llvm is very conservative to move memory read from array/structure/global variable/heap variable
%outside the loop.
%what we do is if the read address is loop invariant, and there are no other write possibly 
%write to the same place, we will not record the memory read.
